Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-29 paper-ieee-trans.tex
minor fix

In this section, we detail the level of knowledge requested in delivering reliable software in order 
to understand the effort employed in the EC-funded software projects over time. We divide literature 
into four different domains that intersect this work: 1) software requirements analysis, 2) software
coding,
3) metrics and measurements, 4) testing.

>>>>

In this section, we detail the level of knowledge requested in delivering reliable software in order 
to understand the effort employed in the EC-funded software projects over time. We divide the literature 
into four different domains that intersect this work: 1) software requirements analysis, 2) software
coding,
3) metrics and measurements, 4) testing.
